### 2017-11-26 paper/sections/1_introduction.tex
paper: addresses #39
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Storage systems use software-based caches extensively to improve performance
but the policies that guide what data to evict and when to evict vary with the
use case. For example, caching file system metadata on clients and servers
reduces the number of remote procedure calls and improves the performance of
create-heavy workloads common in HPC~\cite{ren:sc2014-indexfs,
patil:fast2011-giga+}. But these the policies for when to evict and what data
to evict are specific to the application's behavior so a new use case may prove
to be poor a match for the selected caching
policy~\cite{xiao:socc15-shardfs,brandt:msst2003-lh,sevilla:sc15-mantle,
weil:sc2004-dyn-metadata, weil:osdi2006-ceph}. In this paper, we evaluate a
variety of caching policies using a data management language/policy engine and
arrive at a customized policy that works well for our target application.  This
process of trying general policies and quickly iterating to a customized
solution shows that our prototype can adapt to different of workloads.

@@

Our target application is ParSplice~\cite{perez:jctc20150parsplice}, a
molecular dynamics simulation that uses a hierarchy of caches and a single
persistent key-value store to store both observed minima across a molecule's
equation of motion (EOM) and the hundreds or thousands of partial trajectories
calculated each second during a parallel job.  The fine-grained data annotation
capabilities provided by key-value storage is a natural match for scientific
simulations like ParSplice. But these simulations rely on a mesh-based
decomposition of a physical region and result in millions or billions of mesh
cells, where each cell contains materials, pressures, temperatures and other
characteristics that are required to accurately simulate phenomena of interest.
Unfortunately, this simulations of this size saturate the capacity and bandwidth
capabilities of a single node so we need more effective data management
techniques, such as cache management or load balancing across a cluster.

@@

The biggest challenge for ParSplice is properly sizing the caches in the
storage hierarchy.  The memory usage for a single cache that stores molecule
coordinates is shown in Figure~\ref{fig:cache-management}, where the thin solid
lines marked with \(\times\)'s are the existing configurations in ParSplice.
The default configuration uses an unlimited sized cache, shown by the ``No
Cache Management" line, but using this much memory for one cache is
unacceptable for HPC environments, where a common goal is to keep memory for
such data structures below 3\%\footnote{Anecdotally, we find this threshold
works well for most applications.  For reference, a 1GB cache for a distributed
file system is too large in LANL deployments.}. Since ParSplice deploys a cache
per 300 worker processes, large simulations will not scale. Users can configure
ParSplice to evict data when the cache reaches a threshold but this solution
requires tuning and parameter sweeps; the ``Cache (too small)" curve in
Figure~\ref{fig:cache-management} shows how a poorly configured cache can save
memory but at the expense of performance.  Even worse, this threshold changes
with different initial configurations and clusters so tuning needs to be done
for all system permutations.  Our dynamically sized cache, shown by the think
line in Figure~\ref{fig:cache-management}, detects key access patterns and
re-sizes the cache accordingly.  Without tuning or parameter sweeps, our
solution saves more memory than a hand-tuned cache with a negligible
performance degradation (within the baseline's standard deviation) and works
for a variety of initial conditions.

>>>>

Storage systems use software-based caches extensively to improve performance
but the policies that guide what data to evict and when to evict vary with the
use case. For example, caching file system metadata on clients and servers
reduces the number of remote procedure calls and improves the performance of
create-heavy workloads common in HPC~\cite{ren:sc2014-indexfs,
patil:fast2011-giga+}. But these the policies for when to evict and what data
to evict are specific to the application's behavior and the system's
configuration (hardware, settings, etc.) so a new use case may prove to be a
poor match for the selected caching
policy~\cite{xiao:socc15-shardfs,brandt:msst2003-lh,sevilla:sc15-mantle,
weil:sc2004-dyn-metadata, weil:osdi2006-ceph}. In this paper, we evaluate a
variety of caching policies using a data management language/policy engine and
arrive at a customized policy that works well for our target application.  This
process of trying general policies and quickly iterating to a customized
solution shows that our prototype can adapt to different workloads.

@@

Our target application, ParSplice~\cite{perez:jctc20150parsplice}, is
representative of these types of applications. ParSplice is a molecular
dynamics simulation that uses a hierarchy of caches and a single persistent
key-value store to store both observed minima across a molecule's equation of
motion (EOM) and the hundreds or thousands of partial trajectories calculated
each second during a parallel job.  The fine-grained data annotation
capabilities provided by key-value storage is a natural match for scientific
simulations like ParSplice. But these simulations rely on a mesh-based
decomposition of a physical region and result in millions or billions of mesh
cells, where each cell contains materials, pressures, temperatures and other
characteristics that are required to accurately simulate phenomena of interest.
Unfortunately, simulations of this size saturate the capacity and bandwidth
capabilities of a single node so we need more effective data management
techniques, such as cache management or load balancing across a cluster.

@@

The biggest challenge for ParSplice is properly sizing the caches in the
storage hierarchy.  The memory usage for a single cache that stores molecule
coordinates is shown in Figure~\ref{fig:cache-management}, where the thin solid
lines marked with \(\times\)'s are the existing configurations in ParSplice.
The default configuration uses an unlimited sized cache, shown by the ``No
Cache Management" line, but using this much memory for one cache is
unacceptable for HPC environments, where a common goal is to keep memory for
such data structures below 3\%\footnote{Anecdotally, we find this threshold
works well for HPC applications.  For reference, a 1GB cache for a distributed
file system is too large in LANL deployments.}. Since ParSplice deploys a cache
per 300 worker processes, large simulations will not scale.  Users can
configure ParSplice to evict data when the cache reaches a threshold but this
solution requires tuning and parameter sweeps; the ``Cache (too small)" curve
in Figure~\ref{fig:cache-management} shows how a poorly configured cache can
save memory but at the expense of performance.  Even worse, this threshold
changes with different initial configurations and clusters so tuning needs to
be done for all system permutations.  Our dynamically sized cache, shown by the
think line in Figure~\ref{fig:cache-management}, detects key access patterns
and re-sizes the cache accordingly.  Without tuning or parameter sweeps, our
solution saves more memory than a hand-tuned cache with a negligible
performance degradation (within the baseline's standard deviation) and works
for a variety of initial conditions.

### 2017-11-26 paper/sections/5_file-systems.tex
paper: fix section 6 headings, add lustre trace
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: addresses #39
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

In the previous section, we used our data management language and the Mantle
policy engine to design effective cache management strategies for a new service
and domain. In this section, we compare and contrast the policies examined for
file system metadata load balancing in~\cite{sevilla:sc15-mantle} with the ones
designed for cache management in ParSplice. The similarities show how the
``when"/``where"/``how much" abstractions, data management language, and policy
engine may be widely applicable to other data management techniques, such as
QoS, scheduling, and batching.

\subsection{Using File System Policies for ParSplice}

@@

\subsection{Using ParSplice Policies for File Systems}

@@

% Load balancing in FSs
Mantle was designed for file system metadata load balancing across a cluster of
dedicated metadata servers, where spreading requests across servers improves
performance. But another technique to reduce request load is caching. If
clients and servers maintain a consistent cache, the client can do operations
locally without contacting the metadata server.  The caches in CephFS have the
same performance and utilization trade-off as ParSplice, where large caches
improve performance at the expense of a higher memory footprint. High memory
utilization is problematic when a single metadata server maintains consistent
caches with many clients.  Using cache management policies from the previous
two sections has two benefits for load balancing: (1) increases the capacity of
a single metadata server, and (2) helps identify which parts of the cache to
keep local to a server. For example, applying the key access pattern
detection algorithm from Section~\S\ref{sec:regime-detection} to a similar file
system access pattern has the potential to identify when to migrate keys and
how many keys to migrate.

@@

% other use cases caches/tiers 
Ceph has many other data management techniques that would benefit from the
caching policies developed in Sections~\S\ref{sec:arch-specific}
and~\ref{sec:dom-specific}. Administrators can use the policies in ParSplice to
automatically size and manage cache
tiers\footnote{http://docs.ceph.com/docs/master/rados/operations/cache-tiering/},
caching on object storage devices, or in the distributed block
devices\footnote{http://docs.ceph.com/docs/master/rbd/rbd-config-ref/}.
Integration with Mantle would be straightforward as it is merged into Ceph's
mainline\footnote{http://docs.ceph.com/docs/master/cephfs/mantle/} and the
three caching subsystems mentioned above already maintain key access
traces. We hypothesize that since this is all software defined caching,
something more clever than LRU would improve cache utilization without
sacrificing too much performance.

>>>>

In the previous section, we used our data management language and the Mantle
policy engine to design effective cache management strategies for a new service
and domain. In this section, we compare and contrast the policies examined for
file system metadata load balancing in~\cite{sevilla:sc15-mantle} with the ones
we designed and evaluated above for cache management in ParSplice. The
similarities show how the ``when"/``where"/``how much" abstractions, data
management language, and policy engine may be widely applicable to other data
management techniques, such as QoS, scheduling, and batching.

\subsection{Using Load Balancing Policies for Cache Management}

@@

\subsection{Using Cache Management Policies for Load Balancing}

@@

% Load balancing in FSs
The abstractions in Mantle were designed for file system metadata load
balancing across a cluster of dedicated metadata servers, where spreading
requests across servers improves performance. But another technique to reduce
request load is caching. If clients and servers maintain a consistent cache,
the client can do operations locally without contacting the metadata server.
The caches in CephFS have the same performance and utilization trade-off as
ParSplice, where large caches improve performance at the expense of a higher
memory footprint. High memory utilization is problematic when a single metadata
server maintains consistent caches with many clients.  Using cache management
policies from the previous two sections has two benefits for load balancing:
(1) increases the capacity of a single metadata server, and (2) helps identify
which parts of the cache to keep local to a server. For example, applying the
key access pattern detection algorithm from
Section~\S\ref{sec:regime-detection} to a similar file system access pattern
has the potential to identify when to migrate keys and how many keys to
migrate.

@@

% other use cases caches/tiers 
Storage systems have many other data management techniques that would benefit
from the caching policies developed in Sections~\S\ref{sec:arch-specific}
and~\ref{sec:dom-specific}. For example, Ceph administrators can use the
policies in ParSplice to automatically size and manage cache
tiers\footnote{http://docs.ceph.com/docs/master/rados/operations/cache-tiering/},
caching on object storage devices, or in the distributed block
devices\footnote{http://docs.ceph.com/docs/master/rbd/rbd-config-ref/}.
Integration with Mantle would be straightforward as it is merged into Ceph's
mainline\footnote{http://docs.ceph.com/docs/master/cephfs/mantle/} and the
three caching subsystems mentioned above already maintain key access traces. We
hypothesize that since this is all software defined caching, something more
clever than LRU would improve cache utilization without sacrificing too much
performance.
